Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-19 paper/paper.tex
first stab at the abstract Tested everything on quipu.

\begin{abstract}
  The dynamics of the Min-protein system help Escherichia coli
  bacteria regulate the process of cell division by identifying the
  center of the cell.  We model the Min-protein system in bacteria
  that have been forced into unusual flattened shapes, as have
  recently been experimentally observed.  We find that although the
  presence of Min oscillations is robust in a wide variety of cellular
  configurations, the location of the peaks is strongly affected by
  the cellular shape.  In some cases no periodic oscillations are
  observed.  In particular, we find that cellular shapes observed
  experimentally to present irregular oscillations do so in the
  theoretical model, consistently \fixme{or inconsistently?} with
  experiment.  \fixme{In agreement with previous theoretical and
    experimental results, we observe ``rotating'' behavior in certain
    shapes having three corners.}
\end{abstract}

>>>>

\begin{abstract}
  The dynamics of the Min-protein system help \emph{Escherichia coli}
  regulate the process of cell division by identifying the center of
  the cell.  While this system usually exhibits robust polar
  oscillations in a variety of cell shapes, new experiments have shown
  that when the cells are mechanically deformed into wide, flattened
  out, irregular shapes, the robust regularity of this oscillatory
  behavoir is no longer seen. Here we study widely used stochastic and
  deterministic models of Min-system simulation within these new cell
  shapes.  The deterministic model is seen to be largely inadequate in
  reproducing the qualitatively irregular behavoir, while the
  stochastic model, based on the same differential equations, is able
  to accurately predict what has been seen.  We also conclude that it
  is indeed the irregularity of the cell shape that is responsible for
  the irregular oscillation behavoir, as opposed to the newly deformed
  cells' increased width and altered aspect ratio.
\end{abstract}
